
\subsection{Mechanical structure}
The design of the robot is influenced by the LEGO\textregistered Mindstorms\textregistered EV3 set. While the original set has a movable base it was too small and without an arm with a manipulator. It also does not incorporate the Dynamixel AX-12A Smart Servos used in the final design so the decision to redesign the robot while taking design inspiration from the LEGO\textregistered EV3 design. By developing and designing a new platform it gives the possibility to adapt the dimensions and fastenings for manufacturing methods such as 3D-printing and Laser cutting. 
Consisting of seven Dynamixel\textregistered AX-12A Smart Servos for actuation, two on the base for locomotion and four on the arm and one for the gripping tool the robot has seven degrees of freedom. The main advantage of using the AX-12As is the possibility of connecting them in series which enables pararell control of all the joints. Additionaly with the built in sensors the motors return feedback of the joint angles, angular speed, current draw, teperature to name a few. 

ADD PICTURE OF CONCEPT; WRITE ABOUT THE TOP SPEED AND TURN RADIUS. ALSO HOW LONG IS THE ARM.

\subsection{Electrical components}
While the mechanical components are those visible it's the underlying electrical components that play the biggest role. The internals in the AX-12As give feedback on the state of the motors, the 1000mAh LiPo battery supplies power to the motors and surrounding electronics. For the computanions the NVIDIA\textregistered Jetson Nano is used as it runs Ubuntu natively which makes the implementation of the underlying Robotic Operating System (ROS) \cite{ros} faster.  
\input{tikz/electrical_connections.tex}



